%%%%%
%%
%% This file creates the Item, ItemPacket, ItemFold, ItemEnvelope, and
%% ItemLabel datatypes, and creates macros for each.  These are for
%% various types of in-game items.
%%
%%%%%


%%%%%
%% Item macros are for normal item cards.
\DECLARESUBTYPE{Item}{TransElement}
\PRESETS{Item}{
  \FD\MYtext	{} %% longer text of item
  \FD\MYmark	{} %% possible contents of shaded ``mark'' on card
  \FD\MYbulky	{0} %% potential bulkiness
  \FD\MYcapacity{N/A} %% potential capacity
  \sd\MYlistmap	{\item\MYname\ifx\MYnumber\empty\else\ (\MYnumber)\fi}
  }


%%%%%
%% \prop
%% \unstash
%% \bulky{<number>}
%% \contain{<number>}
%%
%% \prop inside an Item macro labels the card as a prop.  \unstash
%% labels the card as unstashable.  \bulky{n} labels the card as
%% n-hands bulky.  \contain{n} labels the card with n-hands capacity.
\def\prop{%
  \append\MYmark{ ~PROP~ }}
\def\unstash{%
  \append\MYmark{ ~UNSTASHABLE~ }}
\def\bulky#1{%
  \s\MYbulky{#1}%
  \append\MYmark{\mbox{ ~\MYbulky-Hand~Bulky~ }}}
\def\contain#1{%
  \s\MYcapacity{#1}%
  \append\MYmark{\mbox{ ~\MYcapacity-Hand~Capacity~ }}}


%%%%%
%% ItemPacket macros are for item cards with an attached packet.
%% They are a subtype of Item.
\DECLARESUBTYPE{ItemPacket}{Item}
\PRESETS{ItemPacket}{
  \F\MYcontents
  }


%%%%%
%% ItemFold macros are for items represented by just a folded packet.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemFold}{ItemPacket}
\PRESETS{ItemFold}{
  \s\MYmark{}
  }


%%%%%
%% ItemEnvelope macros are for items represented by just an envelope.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemEnvelope}{ItemPacket}
\PRESETS{ItemEnvelope}{
  \s\MYmark{}
  }


%%%%%
%% ItemLabel macros are for small labels that would get used on
%% physreps, e.g. gun labels.  The ``mark'' is left blank, since
%% it isn't used for these.
\DECLARESUBTYPE{ItemLabel}{Item}
\PRESETS{ItemLabel}{
  \s\MYmark{}
  }


%%%%%
%% \icard[<extras>]{<name>}{<number>}{<text>}
%% \specialicard[<extras>]{<name>}{<number>}{<text>}{<mark>}
%% \itempacket[<extras>]{<name>}{<number>}{<text>}{<mark>}{<contents>}
%% \itemfold{<name>}{<number>}{<text>}{<contents>}
%% \itemenvelope{<name>}{<number>}{<text>}{<contents>}
%% \itemlabel{<name>}{<number>}{<text>}
%%
%% These are wrappers around \INSTANCE, useful for 1-shots.
%%
%% For \icard, \specialicard, and \itempacket, the optional <extras>
%% (in []'s) is for things like \unstash and \bulky{3}.  For example,
%% \icard[\prop\contain{2}]{..}{..}{..}{..} gives an item that has a
%% prop and 3-hands capacity.
%%
%% The last arg (#5) to \specialicard is for anything extra you may
%% want in the ``mark''
\newinstance{Item}{\icard[4][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}#1}
\newinstance{Item}{\specialicard[5][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}#1}
\newinstance{ItemPacket}{\itempacket[6][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}\s\MYcontents{#6}#1}
\newinstance{ItemFold}{\itemfold[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemEnvelope}{\itemenvelope[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemLabel}{\itemlabel[3]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Item}{\iTest}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item Card}
  }

\NEW{ItemFold}{\iTestFold}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemFold}{\iTestEnvelope}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemLabel}{\iTestLabel}{
  \s\MYname	{Test Gun Label}
  \s\MYnumber	{0000}
  \s\MYtext	{Disc gun, loadable to 20 shots.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Item}{\iTBankNote}{
  \s\MYname	{Bank Note}
  \s\MYnumber	{}
  \s\MYtext	{This is worth the Kallipolis equivalent of one hundred thousand US dollars, and is backed and signed by the royal treasury.}
  }
	
	\NEW{Item}{\iSBankNote}{
  \s\MYname	{Bank Note}
  \s\MYnumber	{}
  \s\MYtext	{This is worth the Kallipolis equivalent of five thousand US dollars, and is backed and signed by the central bank.}
  }
	
	\NEW{Item}{\iMBankNote}{
  \s\MYname	{Bank Note}
  \s\MYnumber	{}
  \s\MYtext	{This is worth the Kallipolis equivalent of one million US dollars, and is backed and signed by Markos.}
  }
	
	\NEW{Item}{\iGoldEarring}{
  \s\MYname	{Golden Earrings}
  \s\MYnumber	{}
  \s\MYtext	{These are clearly very valuable.}
  }
	
	\NEW{Item}{\iGoldRing}{
  \s\MYname	{Grandmother Agatha's Golden Ring}
  \s\MYnumber	{}
  \s\MYtext	{This is clearly very valuable.}
  }
	
	\NEW{Item}{\iGoldNecklace}{
  \s\MYname	{Grandmother Alexandra's Golden Necklace}
  \s\MYnumber	{}
  \s\MYtext	{This is clearly very valuable.}
  }
	
	\NEW{Item}{\iPoorOuzo}{
  \s\MYname	{Poor Man's Ouzo}
  \s\MYnumber	{}
  \s\MYtext	{A too-strong alcoholic beverage. Causes one Mental Damage -- Drugs. Satisfies any alcohol addiction.}
  }


\NEW{Item}{\iHandwritingSample}{
  \s\MYname	{Strange Document}
  \s\MYnumber	{}
  \s\MYtext	{An odd scroll with strange glyphs on it. It seems to be in some form of code.}
  }
	
\NEW{Item}{\iTruthUrn}{
  \s\MYname	{The Urn of Revelation}
  \s\MYnumber	{}
  \s\MYtext	{A large vessel for a potent truth serum. After drinking from it, you may only speak the truth for two minutes, and are compelled to answer the first yes or no question you are asked.}
  }

\NEW{Item}{\iBlueDart}{
  \unstash{}
  \s\MYname	{Poisoned Blue Dart}
  \s\MYnumber	{}
  \s\MYtext	{May be used to incapacitate any character with a blue headband. The dart will knock the player unconscious in 10 seconds. After five minutes, the victim may be revived by Conclave auxilaries but will no longer be eligible for rulership. Using this dart restores one mental health. May not be transferred.}
  }

\NEW{Item}{\iBlueAntidote}{
  \unstash{}
  \s\MYname	{Blue Antidote Vial}
  \s\MYnumber	{}
  \s\MYtext	{May be used to revive any character with a blue headband knocked out by a dart. Administering the vial takes 30 seconds. Administering a vial can only be interrupted with a brawl. May not be transferred.}
  }
	
\NEW{Item}{\iYellowDart}{
  \unstash{}
  \s\MYname	{Poisoned Yellow Dart}
  \s\MYnumber	{}
  \s\MYtext	{May be used to incapacitate any character with a yellow headband. The dart will knock the player unconscious in 10 seconds. After five minutes, the victim may be revived by Conclave auxilaries but will no longer be eligible for rulership. Using this dart restores one mental health. May not be transferred.}
  }

\NEW{Item}{\iYellowAntidote}{
  \unstash{}
  \s\MYname	{Yellow Antidote Vial}
  \s\MYnumber	{}
  \s\MYtext	{May be used to revive any character with a yellow headband knocked out by a dart. Administering the vial takes 30 seconds. Administering a vial can only be interrupted with a brawl. May not be transferred.}
  }
	
\NEW{Item}{\iAdvisorToken}{
  \s\MYname	{Advisor Token}
  \s\MYnumber	{}
  \s\MYtext	{Each token makes it easier to become the advisor of Kallipolis. This can be sacrificed but not traded.}
  }

\NEW{Item}{\iInfluenceToken}{
  \s\MYname	{Influence Token}
  \s\MYnumber	{}
  \s\MYtext	{Your vote counts twice in the final election. You cannot have more than one influence token. This can be sacrificed but not traded.}
  }

\NEW{Item}{\iGossipToken}{
  \s\MYname	{Gossip Token}
  \s\MYnumber	{}
  \s\MYtext	{You may spend this token to ask an auxiliary for information from Pythias' files on another participant in the Conclave. Alternatively, you may know who they are voting for or their Trial of Trust puzzle piece.}
  }

\NEW{Item}{\iBetterTruthSerum}{
  \s\MYname	{Official Truth Serum}
  \s\MYnumber	{}
  \s\MYtext	{ \emph{The bearer of this potion may order Iris to force another participant to drink this potion.} Drinking this potion deals one Mental Damage -- Migraine. For the next five minutes you can only speak truthfully. You are compelled to answer the first three yes or no questions asked by anyone.}
  }

\NEW{Item}{\iSword}{
  \s\MYname	{Xiphos}
  \s\MYnumber	{}
  \s\MYtext	{ A fearsome, double-edged sword.}
  }
	
\NEW{Item}{\iDagger}{
  \s\MYname	{Kopis}
  \s\MYnumber	{}
  \s\MYtext	{ A small, concealable dagger with Philosopher-Queen Pythias' seal engraved on the hilt. The blade is coated in a thin layer of single-use poison.}
  }
		
\NEW{Item}{\iMetaxa}{
  \s\MYname	{Metaxa}
  \s\MYnumber	{}
  \s\MYtext	{A delicious, smooth alcoholic beverage typically only accessible to the upper class of Kallipolis. This drink satisfies any alcohol addiction.}
  }
		
\NEW{Item}{\iRefinedOpium}{
  \s\MYname	{Refined Opium}
  \s\MYnumber	{}
  \s\MYtext	{An expensive, refined source of opium. This satisfies any opium addiction.}
  }
	
\NEW{Item}{\iRestorativeTonic}{
  \s\MYname	{Restorative Tonic}
  \s\MYnumber	{}
  \s\MYtext	{Ten minutes after drinking this, recover one physical health.}
  }

\NEW{Item}{\iPowerfulOuzo}{
  \s\MYname	{Powerful Ouzo}
  \s\MYnumber	{}
  \s\MYtext	{A crude alcoholic beverage. Take one Mental Damage -- Drugs. This drink satisfies any alcohol addiction.}
  }

\NEW{Item}{\iIntenseOuzo}{
  \s\MYname	{Intense Ouzo}
  \s\MYnumber	{}
  \s\MYtext	{A crude alcoholic beverage. Take one Physical Damage -- Alcohol. This drink satisfies any alcohol addiction.}
  }

	
\NEW{Item}{\iLiquidOpium}{
  \s\MYname	{Liquid Opium}
  \s\MYnumber	{}
  \s\MYtext	{A crude source of opium. Take one Mental Damage -- Drugs. This drink satisfies any opium addiction.}
  }

\NEW{Item}{\iVileMixture}{
  \s\MYname	{Vile Mixture}
  \s\MYnumber	{}
  \s\MYtext	{A strong toxin masked by sugar and spices.  Drinking this causes immediate vomiting and obvious physical weakness. Your physical health immediately drops to 1.}
  }
	
\NEW{Item}{\iTruthSerum}{
  \s\MYname	{Truth Serum}
  \s\MYnumber	{}
  \s\MYtext	{Take one Mental Damage -- Migraine. For the next five minutes you can only speak truthfully. You are compelled to answer the first three yes or no questions asked by anyone.}
  }

\NEW{Item}{\iRuinedIntoxicant}{
  \s\MYname	{Gross Tonic}
  \s\MYnumber	{}
  \s\MYtext	{A hint of alcohol and opium masked by a vomit-inducing syrup. Take one Mental Damage -- Toxic and one Physical Damage -- Toxic. This drunk does not satisfy any addictions.}
  }

\NEW{Item}{\iTA}{
  \s\MYname	{Trial of Trust Puzzle Piece A}
  \s\MYnumber	{}
  \s\MYtext	{ Hoplites are stronger than Lancers. \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTB}{
  \s\MYname	{Trial of Trust Puzzle Piece B}
  \s\MYnumber	{}
  \s\MYtext	{ Hoplites are stronger than Archers.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTC}{
  \s\MYname	{Trial of Trust Puzzle Piece C}
  \s\MYnumber	{}
  \s\MYtext	{ When attacking, diversity in the types of units is essential.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTD}{
  \s\MYname	{Trial of Trust Puzzle Piece D}
  \s\MYnumber	{}
  \s\MYtext	{ The Bireme is the fastest ship which is vital for offense.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTE}{
  \s\MYname	{Trial of Trust Puzzle Piece E}
  \s\MYnumber	{}
  \s\MYtext	{ A naval defense is strongest with exactly two naval vessels.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTF}{
  \s\MYname	{Trial of Trust Puzzle Piece F}
  \s\MYnumber	{}
  \s\MYtext	{ The Penteconter is vital for defense, but not the best choice for offense.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTG}{
  \s\MYname	{Trial of Trust Puzzle Piece G}
  \s\MYnumber	{}
  \s\MYtext	{ Exactly one siege weapon is best for both defense and offense.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTH}{
  \s\MYname	{Trial of Trust Puzzle Piece H}
  \s\MYnumber	{}
  \s\MYtext	{ Catapults are interior on both offense and defense.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
\NEW{Item}{\iTI}{
  \s\MYname	{Trial of Trust Puzzle Piece I}
  \s\MYnumber	{}
  \s\MYtext	{ When defending, the Bireme is an inferior ship.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
	\NEW{Item}{\iTJ}{
  \s\MYname	{Trial of Trust Puzzle Piece J}
  \s\MYnumber	{}
  \s\MYtext	{ First light and midnight are bad times to attack -- the enemy will see or hear you coming too easily.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
	\NEW{Item}{\iTK}{
  \s\MYname	{Trial of Trust Puzzle Piece K}
  \s\MYnumber	{}
  \s\MYtext	{ It is foolish to attack at first light or high noon; the enemy will be well rested and you will have undergone a tough march. \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
	\NEW{Item}{\iTL}{
  \s\MYname	{Trial of Trust Puzzle Piece L}
  \s\MYnumber	{}
  \s\MYtext	{ Artemis is angered by an attack at high noon as she cannot watch, and Apollo is angered by an attack at midnight as he cannot watch.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
	\NEW{Item}{\iTM}{
  \s\MYname	{Trial of Trust Puzzle Piece M}
  \s\MYnumber	{}
  \s\MYtext	{ The battering ram complements melee troops well.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }
	
	\NEW{Item}{\iTN}{
  \s\MYname	{Trial of Trust Puzzle Piece N}
  \s\MYnumber	{}
  \s\MYtext	{ Exactly one melee type is best for offense, and none is needed on defense.  \\* -- \\* \textbf{This statement represents spoken information and cannot be directly shown to anyone for any reason.}  }
  }