%%%%%
%%
%% This file sets up the Sign and Label datatypes and creates Sign and
%% Label macros.
%%
%% Signs generally represent interesting parts of game area, usually
%% as things posted on walls.  Labels represent other things, often on
%% or inside envelopes, that are part of complex mechanics.
%%
%% The default value for \MYloc will inherit location from the Place
%% or Sign most immediately up the ownership tree.  Override this by
%% setting \MYloc to anything (even blank).
%%
%% Sign is for full-sized signs that would cover most of a large
%% manila envelope; SignMedium is for signs sized to half-sized manila
%% envelopes; SignSmall is for signs sized for small manila envelopes
%% (the same size as item cards).  Label, LabelMedium, and LabelSmall
%% are analagous, but they don't have a \takedownby note at the
%% bottom.  You can always use a sign or label without an envelope or
%% with a differently-sized envelope.  Choose which based on
%% visibility and content.
%%
%% SignTiny is for signs you want to be hard to find; it is small and
%% does not have a \takedownby note.  SignDot is for a very small
%% "dot" which only has a title.
%%
%% SignStrip produces a strip of paper (without a \takedownby note)
%% with labels on the outside that show on both sides if you fold it
%% in half.  These are a convenient alternative to sub-envelopes. They
%% can also be used for "s-packets" taped to walls (see
%% Extras/README-s-packets).
%%
%% LabelCover produces a label similar to the cover to a research
%% notebook.  LabelPage, likewise, produces a page.
%%
%% EOG is for full-sized end-of-game signs.
%%
%%%%%

\DECLARESUBTYPE{Sign}{Element}
\PRESETS{Sign}{
  \FD\MYloc	{\mylocation} %% real-space location
  \FD\MYtext	{} %% text of sign
  }
\POSTSETS{Sign}{
  \edef\mylocation{\MYloc}
  \protected@edef\@ownerstring{%
    \MYname%
    \ifx\mylocation\empty\else\ (\mylocation)\fi%
    }
  }
\def\mylocation{}

\def\loc 1{\rs\MYloc{ 1}}

\DECLARESUBTYPE{SignMedium}{Sign}
\DECLARESUBTYPE{SignSmall}{Sign}
\DECLARESUBTYPE{SignTiny}{Sign}
\DECLARESUBTYPE{SignDot}{Sign}
\PRESETS{SignDot}{\s\MYtext{}}

\DECLARESUBTYPE{Label}{Sign}
\PRESETS{Label}{\s\MYloc{}}
\DECLARESUBTYPE{LabelMedium}{Label}
\DECLARESUBTYPE{LabelSmall}{Label}

\DECLARESUBTYPE{SignStrip}{Sign}
\DECLARESUBTYPE{LabelCover}{Label}
\DECLARESUBTYPE{LabelPage}{Label}

\DECLARESUBTYPE{EOG}{Sign}
\PRESETS{EOG}{%
  \s\MYname	{End Of Game}
  \s\MYtext	{{\bf\Huge You may not pass through here.}}
  }


%%%%%
%% \signbig[<location>]{<name>}{<text>}
%% \eog[<location>]
%%
%% \signmdeium[<location>]{<name>}{<text>}
%% \signsmall[<location>]{<name>}{<text>}
%% \signtiny[<location>]{<name>}{<text>}
%% \signdot[<location>]{<name>}
%%
%% \labelbig{<name>}{<text>}
%% \labelmedium{<name>}{<text>}
%% \labelsmall{<name>}{<text>}
%%
%% \signstrip[<location>]{<name>}{<text>}
%% \labelcover{<name>}{<text>}
%% \labelpage{<name>}{<text>}
\newinstance{Sign}{\signbig[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{EOG}{\eog[1][\mylocation]}{\s\MYloc{ 1}}

\newinstance{SignMedium}{\signmedium[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignSmall}{\signsmall[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignTiny}{\signtiny[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{SignDot}{\signdot[2][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}}

\newinstance{Label}{\labelbig[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelMedium}{\labelmedium[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelSmall}{\labelsmall[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}

\newinstance{SignStrip}{\signstrip[3][\mylocation]}{
  \s\MYloc{ 1}\s\MYname{ 2}\s\MYtext{ 3}}
\newinstance{LabelCover}{\labelcover[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}
\newinstance{LabelPage}{\labelpage[2]}{
  \s\MYname{ 1}\s\MYtext{ 2}}


%%%%%
%% \sEOG{}
%% use \sEOg[\loc{<location>}]{} for EOG sign at a specific place
\NEW{EOG}{\sEOG}{
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Sign}{\sLab}{
  \s\MYname	{An Apothecary Lab}
  \s\MYtext	{A well-stocked laboratory filled with apothecary equipment.}
  }

\NEW{Sign}{\sLabBurner}{
  \s\MYname	{A flame burner}
 \s\MYtext	{Drinks can be brewed on this burner. Only one drink can be brewed at a time. Anyone may remove the drink from the burner but you must write the current time on the flask and you may not look at the contents of the flask.}
  }

\NEW{Sign}{\sLabSupplies}{
  \s\MYname	{General Apothecary Lab Supplies}
 \s\MYtext	{Only an apothecary may look under this sign.}
 \s\MYitems	{ \multi{6}{\iRestorativeTonic{}}
						  \multi{5}{\iPowerfulOuzo{}}
							\multi{5}{\iIntenseOuzo{}}
							\multi{6}{\iLiquidOpium{}}
							\multi{6}{\iVileMixture{}}
							\multi{3}{\iTruthSerum{}}
							}
  }
	
\NEW{Sign}{\sMedeaSupplies}{
 \s\MYname	{Medea's Specialized Lab Supplies}
 \s\MYtext	{Only Medea the Doctor may look under this sign.}
 \s\MYitems	{ \multi{3}{\iFalseAlcohol{}} \multi{3}{\iFalseOpium{}} \multi{6}{\iRuinedIntoxicant{}} \multi{4}{\iAddictionSuppressor{}} }
  }
  
\NEW{Sign}{\sCouncilRoom}{
  \s\MYname	{The Chamber of Trials}
  \s\MYtext	{A huge chamber at the center of the temple. All the Trials and election results are announced here. A new trial starts each hour.}
  }

\NEW{Sign}{\sVotingRoom}{
  \s\MYname	{The Chamber of Concensus}
  \s\MYtext	{Twelve urns are here, one for each participant in the Conclave. Auxiliaries are monitoring the urns at all times.
					   You may change your vote at any time. The auxiliaries prevent you from inspecting the contents of an urn or watching anyone else vote.}
  }
	
\NEW{Sign}{\sAdvisorRoom}{
  \s\MYname	{The Seat of the Advisor}
  \s\MYtext	{An imposing statue of Agus, the prime advisor to the first philosopher-king Apostalis. An auxiliary here can accept applications to become the advisor to the newly elected ruler.}
  }
	
\NEW{Sign}{\sAltar}{
  \s\MYname	{The Altar of Sacrifice}
  \s\MYtext	{A grand altar overlooks a small but deep hole leading to a pit of fire. A Priestess of the temple can help make a sacrifice to Artemis and other gods here.}
  }
	
\NEW{Sign}{\sRewards}{
  \s\MYname	{GM Rewards}
  \s\MYtext	{Valuable items offered as rewards for Trials or election status updates.}
	
	\s\MYitems	{ \multi{2}{\iBetterTruthSerum{}}
							  \multi{6}{\iAdvisorToken{}}
						    \multi{3}{\iSeerToken{}}
								\multi{3}{\iGossipToken{}}
								\multi{2}{\iInfluenceToken{}}
								\multi{3}{\iShield{}}
								\multi{3}{\iSword{}}
								\multi{5}{\iMetaxa{}}
								\multi{5}{\iRefinedOpium{}}
								\iDagger{}
								\iTruthUrn{}
								}
  }

\NEW{Sign}{\sVenomBlue}{
  \s\MYname	{Trial of Venom Blue}
  \s\MYtext	{Trial of Venom Blue items.}
	
	\s\MYitems	{ \multi{6}{\iBlueDart{}}
							  \multi{6}{\iBlueAntidote{}}
								}
  }
		
\NEW{Sign}{\sVenomYellow}{
  \s\MYname	{Trial of Venom Yellow}
  \s\MYtext	{Trial of Venom Yellow items.}
	
	\s\MYitems	{ \multi{6}{\iYellowDart{}}
							  \multi{6}{\iYellowAntidote{}}
								}
  }
	
\NEW{Sign}{\sTrust}{
  \s\MYname	{Trial of Trust}
  \s\MYtext	{Trial of Trust items.}
	
	\s\MYitems	{ \iTA{}
							  \iTB{}
								\iTC{}
								\iTD{}
								\iTE{}
								\iTF{}
								\iTG{}
								\iTH{}
								\iTI{}
								\iTJ{}
								\iTK{}
								\iTL{}
								\iTM{}
								\iTN{}
								}
  }

\NEW{Sign}{\sVA}{
  \s\MYname	{Hypatia's Vote}
  \s\MYtext	{Only Hypatia may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVB}{
  \s\MYname	{Hesiodos's Vote}
  \s\MYtext	{Only Hesiodos may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVC}{
  \s\MYname	{Gregorios' Vote}
  \s\MYtext	{Only Gregorios may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVD}{
  \s\MYname	{Sophia's Vote}
  \s\MYtext	{Only Sophia may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVE}{
  \s\MYname	{Medea's Vote}
  \s\MYtext	{Only Medea may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVF}{
  \s\MYname	{Cassius's Vote}
  \s\MYtext	{Only Cassius may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVG}{
  \s\MYname	{Markos' Vote}
  \s\MYtext	{Only Markos may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVH}{
  \s\MYname	{Satyrus' Vote}
  \s\MYtext	{Only Satyrus may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVI}{
  \s\MYname	{Tatania's Vote}
  \s\MYtext	{Only Tatania may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
\NEW{Sign}{\sVJ}{
  \s\MYname	{Nikon's Vote}
  \s\MYtext	{Only Nikon may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
	
\NEW{Sign}{\sVK}{
  \s\MYname	{Helena's Vote}
  \s\MYtext	{Only Helena may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
	
\NEW{Sign}{\sVL}{
  \s\MYname	{Petra's Vote}
  \s\MYtext	{Only Petra may look under this sign. To vote, simply write the name of the person you are voting for on the back of this sheet, crossing out any previous vote. You can only vote for someone who still has a valid urn.}
  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
